Assessing Bicycle Parking Safety in Toronto: The Multifaceted Nature of Theft Risk.

### 2023-10-04 outputs/paper/paper.qmd
Update the in-text citation
Fix the citation errors for tables and figures.

## 1. The Time of Bicycle Thefts Occurrence

The cleaned data contains very detailed information regarding the occurrence time of each theft, detailing up to the specific hour of occurrence. The table below @tbl_theft_occ_year summarize the occurrence year of bicycle thefts.

```{r}
#| echo: false
#| message: false
#| label: tbl_theft_occ_year
#| tbl-cap: Summary of Bicycle Thefts Occurrence Year (2014 to 2022)
cleaned_data %>% 
  group_by(occ_year) %>% 
  summarise(n = n()) %>% 
  arrange(desc(occ_year)) %>% 
  slice(1:9) %>% 
  rename(`Occurrence Year` = occ_year,
         `Count` = n) %>% 
  kable(booktabs = TRUE)
```

@tbl_theft_occ_year shows the number of bicycle thefts from 2009 to 2022. Between 2014 and 2018, we can see that the number of bicycle thefts increased first, then the bicycle thefts dropped gradually since 2019. The reported number of bicycle thefts for last year was about 2400.

## 2. The Premises Place Where the Bike was stolen

The second main category in the cleaned data is the premises type of each bicycle thefts. The premises type here represents the places where the bicycle was stolen. In this data, there are six main premises types of bicycle theft: Commercial, Apartment, Other, House, Educational, Transit, and Other. [@tbl_theft_premises_type] summarizes the number of thefts for each premises type.

```{r}
#| echo: false
#| message: false
#| label: tbl_theft_premises_type
#| tbl-cap: Summary of Bicycle Thefts In Terms of Premises Types

@@

From @tbl_theft_premises_type, we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.

## 3. The Stolen Bicycles' Features

@@

```{r}
#| echo: false
#| message: false
#| label: tbl_theft_bike_cost
#| tbl-cap: Summary of Stolen Bicycle Cost

@@

@tbl_theft_bike_cost shows the bicycle price of stolen bicycles. The mean cost of stolen bikes is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles is worth 120,000 dollars.

@@

```{r}
#| echo: false
#| message: false
#| label: fig_year_trend
#| fig-cap: Number of bicycle thefts from 2017 to 2022 by month

@@

@fig_year_trend compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years. The summer seems to have significantly higher bicycle thefts than winter each year. In addition, July is the most severe month of bicycle thefts each year, ranging from 350 to 550 from the previous years. At the beginning and end of each year, bicycle thefts were always stable, keeping constant around 100.

@@

```{r}
#| echo: false
#| message: false
#| label: fig_premises_type
#| fig-cap: Distribution of Bicycle Thefts by Premises Type and Seasonal Trends in Toronto

@@

@fig_premises_type compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer. There are three facets marking three different years. Each bar in each facet represents the number of bicycle thefts of a premises type. The filled color in each bar shows the proportion of bicycles stolen during the summer, with light coral meaning NO and light grey meaning Yes.

@@

```{r}
#| echo: false
#| message: false
#| label: fig_bike_type
#| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types

@@

@fig_bike_type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types. Each bar represents the corresponding number of bicycles of a bike type under different colors. In addition, each bar is filled with two colors, orange and dark teal, representing the proportion of bicycles that have a price above the mean or below the mean price.

@@

As illustrated in @fig_year_trend, bicycle thefts peak during the summer months and dip in the winter. This seasonal trend aligns with Amanat's observation [@amanat2023] of a 429% surge in thefts during summertime. A plausible explanation for this fluctuation is the increased cycling activity in summer due to favorable weather. Conversely, the cold winter months deter many from cycling, resulting in fewer theft opportunities.

@@

@fig_premises_type provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent. Notably, apartments emerged as the predominant location for such thefts. Yet, there's a discernible decline in apartment-related thefts from 2020 to 2023. In contrast, thefts in open spaces like streets, roads, or highways (categorized as "Outside") have seen a gradual increase, becoming most prevalent in 2022. Educational premises, such as schools or universities, also witnessed an increase in theft incidents, underscoring the need for students to rasie caution when parking their bicycles on campus.

@@

@fig_bike_type reveals a distinct preference among thieves for black bicycles. In fact, the number of stolen black bikes equals to the combined total of the next three colors. In terms of bicycle types, mountain bicycles (MT) is the theives' primary target, closely followed by regular (RG) bicycles, which experience nearly identical theft rates.

>>>>

## The Time of Bicycle Thefts Occurrence

The cleaned data contains very detailed information regarding the occurrence time of each theft, detailing up to the specific hour of occurrence. The table below @tbl-theft-occ-year summarize the occurrence year of bicycle thefts.

```{r}
#| echo: false
#| message: false
#| label: tbl-theft-occ-year
#| tbl-cap: Summary of Bicycle Thefts Occurrence Year (2014 to 2022)
cleaned_data %>% 
  group_by(occ_year) %>% 
  summarise(n = n()) %>% 
  arrange(desc(occ_year)) %>% 
  slice(1:9) %>% 
  rename(`Occurrence Year` = occ_year,
         `Count` = n) %>% 
  kable(booktabs = TRUE)
```

@tbl-theft-occ-year shows the number of bicycle thefts from 2009 to 2022. Between 2014 and 2018, we can see that the number of bicycle thefts increased first, then the bicycle thefts dropped gradually since 2019. The reported number of bicycle thefts for last year was about 2400.

## The Premises Place Where the Bike was stolen

The second main category in the cleaned data is the premises type of each bicycle thefts. The premises type here represents the places where the bicycle was stolen. In this data, there are six main premises types of bicycle theft: Commercial, Apartment, Other, House, Educational, Transit, and Other. @tbl-theft-premises-type summarizes the number of thefts for each premises type.

```{r}
#| echo: false
#| message: false
#| label: tbl-theft-premises-type
#| tbl-cap: Summary of Bicycle Thefts In Terms of Premises Types

@@

From @tbl-theft-premises-type, we can observe that premises types "Outside" and "Apartment" have more bicycle thefts than the rest places, meaning that people need to pay more attention to their bicycles if they park them near the condo or on the street.

## The Stolen Bicycles' Features

@@

```{r}
#| echo: false
#| message: false
#| label: tbl-theft-bike-cost
#| tbl-cap: Summary of Stolen Bicycle Cost

@@

@tbl-theft-bike-cost shows the bicycle price of stolen bicycles. The mean cost of stolen bikes is around 1000 dollars. However, it is surprising that the most expensive stolen bicycles is worth 120,000 dollars.

@@

```{r}
#| echo: false
#| message: false
#| label: fig-year-trend
#| fig-cap: Number of bicycle thefts from 2017 to 2022 by month

@@

@fig-year-trend compares the monthly bicycle thefts from 2017 to 2022, with each line with different colors representing different years. The summer seems to have significantly higher bicycle thefts than winter each year. In addition, July is the most severe month of bicycle thefts each year, ranging from 350 to 550 from the previous years. At the beginning and end of each year, bicycle thefts were always stable, keeping constant around 100.

@@

```{r}
#| echo: false
#| message: false
#| label: fig-premises-type
#| fig-cap: Distribution of Bicycle Thefts by Premises Type and Seasonal Trends in Toronto

@@

@fig-premises-type compares the premises type of bicycle thefts in the recent three years and indicates the proportion of bicycles stolen during the summer. There are three facets marking three different years. Each bar in each facet represents the number of bicycle thefts of a premises type. The filled color in each bar shows the proportion of bicycles stolen during the summer, with light coral meaning NO and light grey meaning Yes.

@@

```{r}
#| echo: false
#| message: false
#| label: fig-bike-type
#| fig-cap: Distribution of bicycle thefts for the Top 4 Colours and Top 5 Bicycle Types

@@

@fig-bike-type compares the number of bicycle thefts for the top 4 colors and top 5 bicycle types. Each bar represents the corresponding number of bicycles of a bike type under different colors. In addition, each bar is filled with two colors, orange and dark teal, representing the proportion of bicycles that have a price above the mean or below the mean price.

@@

As illustrated in @fig-year-trend, bicycle thefts peak during the summer months and dip in the winter. This seasonal trend aligns with Amanat's observation [@amanat2023] of a 429% surge in thefts during summertime. A plausible explanation for this fluctuation is the increased cycling activity in summer due to favorable weather. Conversely, the cold winter months deter many from cycling, resulting in fewer theft opportunities.

@@

@fig-premises-type provides insights into the distribution of bicycle thefts over the years, which remains relatively consistent. Notably, apartments emerged as the predominant location for such thefts. Yet, there's a discernible decline in apartment-related thefts from 2020 to 2023. In contrast, thefts in open spaces like streets, roads, or highways (categorized as "Outside") have seen a gradual increase, becoming most prevalent in 2022. Educational premises, such as schools or universities, also witnessed an increase in theft incidents, underscoring the need for students to rasie caution when parking their bicycles on campus.

@@

@fig-bike-type reveals a distinct preference among thieves for black bicycles. In fact, the number of stolen black bikes equals to the combined total of the next three colors. In terms of bicycle types, mountain bicycles (MT) is the theives' primary target, closely followed by regular (RG) bicycles, which experience nearly identical theft rates.
